Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
minor fix

\begin{algorithm}[]
\scriptsize
\begin{algorithmic}[1]
\Function{$safetyCheck()$}{}
\State assert($ \underline{u}  \leq u \leq \overline{u}$)
 \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
\While ($c=0; c < 2^{Num_States}; c++$)
  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
	\While{$i=0; i< k; i++$}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndWhile
  	\State set $x_0$ to be a new vertex state
  	\EndWhile
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:safetycheck}
\end{algorithm}

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}. We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
%More details on how to model quantization as noise are given in the 
%Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge \phi_{input} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

>>>>

\begin{algorithm}[]
\scriptsize
\begin{algorithmic}[1]
\Function{$safetyCheck()$}{}
\State assert($ \underline{u}  \leq u \leq \overline{u}$)
 \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
\For ($c=0; c < 2^{Num_States}; c++$)
  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
	\While{$i=0; i< k; i++$}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndWhile
  	\State set $x_0$ to be a new vertex state
  	\EndFor
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:safetycheck}
\end{algorithm}

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}. We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
%More details on how to model quantization as noise are given in the 
%Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge \phi_{input} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$
